%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{}{\LARGE Xinghua Pan}} & \href{https://github.com/xhorn-pan}{ \faicon{github} xhorn-pan} \\
  %\href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
  \faicon{envelope} \href{mailto:xhorn.pan@gmail.com}{xhorn.pan@gmail.com} | \faicon{mobile} (352)-872-8387  &  \faicon{code} Python, C/C++  
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
    {University of Florida}{Gainesville, Florida}
    {Master of Science in Computer Engineering;  GPA: 3.85}{Jan. 2019 -- Dec. 2020}

    % add courses
    \begingroup
    \scriptsize
    \begin{tabular*}{\textwidth}{l@{\hspace{1cm}}r@{\hspace{8pt}} l}
       & (Spring 2019):&  Advanced Data Structures, Analysis of Algorithms, Math for Intelligent Systems.\\& (Fall 2019): &Machine Learning, Programming Language Principle, Computer Architect Principle.\\& (Spring 2020):& Embedded Systems, Advanced System Programming, Reconfigurable Computing.\\ & (Fall 2020): & Distributed Operating System Principles.
    \end{tabular*}
    \endgroup
    
    \resumeSubheading
        {China University of Petroleum}{Beijing, China}
        {Master of Science in Computer Science \& Engineering;  GPA: 8.4/10.0}{Sept. 2009 -- July. 2012}
        \resumeSubheading
            {Sichuan University}{Chengdu, China}
            {Bachelor of Science in Applied Chemistry; GPA: 7.8/10.0}{Sept. 2003 -- July. 2007}
            \resumeSubHeadingListEnd

            %-----------EXPERIENCE-----------------
            \section{Experience}
            \resumeSubHeadingListStart

            \resumeSubheading
                {Elex Technology}{Beijing, China}
                {Software/System Engineer}{Jan 2012 - April 2016}
                \resumeItemListStart
                \resumeItem{FullStack}{A Website for IT asset and project management. Utilized Python and AngularJS; used by both the on-call team and developer teams.}
                \resumeItem{DevOps}{Service for sending email and SMS notifications; Utilized Nagios and Ganglia; helped to increase monitor coverage by 30+\%.}
                \resumeItem{IT Budget and Audit}{A tool integrated with Softlayer API and export Excel to report IT costs and in-game pay-log.}
                \resumeItem{OpenStack cluster}{Build and maintain a cluster supporting different developer groups.}
                \resumeItemListEnd

                \resumeSubheading
                    { Petropark Co., Ltd}{Beijing, China}
                    {Software Engineering Intern}{Sept. 2010 - Dec. 2011}
                    \resumeItemListStart
                    \resumeItem{Client Project}{Linux Administrator and Java programming}
                    \resumeItemListEnd

                    \resumeSubHeadingListEnd


                    %-----------PROJECTS-----------------
                    \section{Projects}
                    \resumeSubHeadingListStart
                    \resumeSubItem{A Tweet-like Engine}{The engine utilized Akka.Net Cluster and FSharp; build a JSON based API using WebSharper with WebSocket interface}
                    \resumeSubItem{Red-black tree}{C++ implementation for class: Advanced Data structure. }
                    \resumeSubItem{Lua interpreter(subset)}{Java implementation for class: Programming Language Principle.}
                    \resumeSubItem{Cache Timing and Meltdown attack}{For class: Computer Architecture Principle.}
                    \resumeSubItem{Machine learn model (VAE and GAN) training}{Tensorflow based implementation on a subset of VGG2 dataset, for class: Machine Learning.}
                    \resumeSubItem{Wechat jump(mini game) bot}{A python script using OpenCV object dectection and Android ADB.}
                    \resumeSubItem{Archlinux Setup}{Blog that gives instructions on ArchLinux installation and develop environment setting up on Dell XPS 15 9560.}
                    \resumeSubHeadingListEnd



                    %-----------SKILLS-------------------
                    \section{Programming Skills}
                    \resumeSubHeadingListStart
                    \item{
                        \textbf{Languages}{: Python, C/C++, Java, JavaScript, FSharp, SQL, Rust, VHDL} 
                    }
                    \item{
                        \textbf{Technologies}{: Git, WebSocket, REST API, TensorFlow, \LaTeX, Qt, Flask, Angular, Bootstrap, Akka.Net, FPGA, Vivado}
                    }
                    \resumeSubHeadingListEnd
